An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-08-01 article.tex
abstract

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
%% Text of abstract
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
Using a ten year dataset that spans Australia we describe the relationships of input resources to the output yield and quality of grapes for wine production. Creating a baseline for comparing the efficiency of winegrowers with regard to the tradeoff between invested resources, yield and quality. Showing that economies of scale prevail for optimising crops for yield, with larger crops producing more grapes per area. And, showing that smaller crops utilising less resources are more closely related to quality.
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'
